Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-04-19 intro.tex
2014.10.05 (Vassilis) Clean-up, rewording and reviewing the unstructured section. Efficiency, overhead and scalability definitions reworked in background section.
2015.04.19 (Vassilis) Reformatting using the IEEE LaTeX template. Various integration changes.

\emph{Peer-to-peer} (\p) networks are self-organizing, distributed systems where
participating nodes, called \emph{peers}, act as both resource providers and
resource consumers in contrast to the conventional \emph{client-server} model
where nodes undertake specific roles.
For over a decade, \p\ networks have been widely deployed and have
enjoyed immense popularity from Internet communities, primarily because
of the great number of features they offer to distributed applications 
built atop them. 
Such diverse features include:  high availability and robustness,
load-balancing, quality of service, scalability, decentralized administration,
and anonymity.

@@

% TODO SOME EXTRA REFERENCES IF NEEDED FOR THE USE OF OVERLAYS IN GENERAL
%
% IF ULTIMATELY DELETED CHECK TO REMOVE THE REFERENCES INCLUDED SINCE MOST
% PROBABLY ARE NOT USED ELSEWHERE.
%
%find citation for Narada & Adobe's Real Time Media Flow Protocol (RTMFP)
%\cite{} that provide quality-of-service (QoS) guarantees. \emph{IP
%multicast}, as well as other proposals such as \emph{IntServ} and
%\emph{DiffServ} \cite{cisco_diffserv_2005}, have still not seen wide deployment
%largely due to the fact they require support from the IP
%infrastructure. On the other hand, an overlay network can be deployed on
%end-systems running the overlay protocol software, without the cooperation of ISPs.
%Academic research includes
%\cite{chu_esm_2000,jannotti_overcast_2000,kwon_tag_2002} among others.

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes and logical links
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.6]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}

>>>>

\IEEEPARstart{P}{eer-to-peer (\p)} networks are self-organizing, distributed systems where
participating nodes, called \emph{peers}, act as both resource providers and
resource consumers in contrast to the conventional \emph{client-server} model
where nodes undertake specific roles.
For over a decade, \p\ networks have been widely deployed and have
enjoyed immense popularity from Internet communities, primarily because
of the great number of features they offer to distributed applications 
built atop them. 
Such diverse features include:  high availability and robustness,
load-balancing, quality of service, scalability, decentralized administration,
and anonymity.

@@

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes and logical links
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.53]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}
